Examination of shapes! (homework exam)

### 2016-02-23 geometricAlgorithms/homeworkExam/homeworkExam.tex
trying to draw a custom trianlge

\documentclass{article}
\usepackage{amsmath}
\usepackage{txfonts}
\usepackage{booktabs}
\usepackage{color}
\usepackage{bussproofs}
\usepackage[pdftex]{graphicx}
\DeclareGraphicsRule{*}{mps}{*}{}
\usepackage{pifont}
\usepackage{qtree}
\usepackage{emp}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{svg}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{seqsplit}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\pgfplotsset{
    compat=1.9,
    compat/bar nodes=1.8
}

\newenvironment{scprooftree}[1]%
{\gdef\scalefactor{#1}\begin{center}\proofSkipAmount \leavevmode}%
{\scalebox{\scalefactor}{\DisplayProof}\proofSkipAmount \end{center} }

\newcommand{\brcell}[2][l]{%
	\begin{tabular}[#1]{@{}l@{}}#2\end{tabular}}

% "define" Scala
\lstdefinelanguage{scala}{
  morekeywords={abstract,case,catch,class,def,%
    do,else,extends,false,final,finally,%
    for,if,implicit,import,match,mixin,%
    new,null,object,override,package,%
    private,protected,requires,return,sealed,%
    super,this,throw,trait,true,try,%
    type,val,var,while,with,yield},
  otherkeywords={=>,<-,<\%,<:,>:,\#,@},
  sensitive=true,
  morecomment=[l]{//},
  morecomment=[n]{/*}{*/},
  morestring=[b]",
  morestring=[b]',
  morestring=[b]"""
}
\begin{document}
\begin{empfile}
\begin{empcmds}
input metauml;
\end{empcmds}
\author{Jappie Klooster}
\title{Examination of shapes! (homework exam)}
\maketitle

@@

\begin{figure}
\begin{tikzpicture}[
rotor/.style={inner sep=3pt,outer sep=0,fill opacity=0.3,minimum width=2cm,circle},
crossline/.style={gray,line width=3pt,opacity=0.5,line cap=round}
]
	\node[rotor] (n2) at (4,2)  {\quad y};

	\draw [->,line width=1pt] (n2) ++(140:5mm) arc (-220:40:5mm);
	\draw (1,1) -- (3,1) -- (3,3) -- (1,3) -- (1,1);
	\draw (2,2) -- (0,2) -- (0,1);

	\draw (5,1) -- (7,1) -- (7,3) -- (5,3) -- (5,1);
	\draw (6,2) -- (8,2) -- (8,1);

	\draw (4,0) -- (4,4);
\end{tikzpicture}
\caption{Cube with arm sticking out sillhoutte}
\end{figure}

I did applied similiar rotations for the $x$ and $z$ axis. If you
do both 180 degrees you end up looking at the same side. So for this
particiluar figure there exists a unique $xy$-sillhoutte.

\subsubsection{When it is not unique}

It is not unique when certain parts of the figure can be mirrored. For
example consider the follwoing figure:

\begin{figure}
\begin{tikzpicture}[
rotor/.style={inner sep=3pt,outer sep=0,fill opacity=0.3,minimum width=2cm,circle},
crossline/.style={gray,line width=3pt,opacity=0.5,line cap=round}
]
	\node[rotor] (n2) at (5,2)  {\quad y};

	\draw [->,line width=1pt] (n2) ++(140:5mm) arc (-220:40:5mm);
	\draw (1,1) -- (3,1) -- (3,3) -- (1,3) -- (1,1);
	\draw (2,2) -- (0,2) -- (0,1);
	\draw (2,2) -- (4,2) -- (4,3);

	\draw (7,1) -- (9,1) -- (9,3) -- (7,3) -- (7,1);
	\draw (8,2) -- (10,2) -- (10,1);
	\draw (8,2) -- (6,2) -- (6,3);

	\draw (5,0) -- (5,4);
\end{tikzpicture}
\caption{Cube with two arms in opposite direction sillhoutte}
\end{figure}

The issue with this figue is that if you apply 180 degrees $z$ rotation you
end up with the same sillhoutte. So having some symetry ends up causing will
cause having redundant sillhouttes.

\newpage
\subsection{Give an algorithm that detrmines an $xy$-silhouette of a conves polyhedron $P$ in O(n) time}
%TODO: should we find the side?
%TODO: walk to the side of the silhoutte

@@

\section{Polygon cut}
\section{Diagonal polygon cut}
\end{empfile}
\end{document}

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{pst-solides3d}
\usepackage{auto-pst-pdf}

\begin{document}
\author{Jappie Klooster}
\title{Examination of shapes! (homework exam)}
\maketitle

@@

\begin{pspicture}(-2,-2)(3,3)
\psset{viewpoint=100 30 20,Decran=100}
\axesIIID[showOrigin=false](1,1,1)(3,2,2.5)
\psSolid[object=new,
        action=draw,
        sommets=
		0 2 0
		-2 0 -2
		2 0 -2
		2 0 2
   faces={
       [0 1 2]
       [0 2 3]
       [0 3 1]
       [1 2 3]
       }]%
\end{pspicture}

I did applied similiar rotations for the $x$ and $z$ axis. If you
do both 180 degrees you end up looking at the same side. So for this
particiluar figure there exists a unique $xy$-sillhoutte.
\newpage
\subsection{Give an algorithm that detrmines an $xy$-silhouette of a conves polyhedron $P$ in O(n) time}
%TODO: should we find the side?
%TODO: walk to the side of the silhoutte

@@

\section{Polygon cut}
\section{Diagonal polygon cut}
\end{document}
